Clustering/Orthofinder analysis

### 2022-02-25 analysis/Orthofinder.Rmd
Fix typo

fileConn<-file('Genes_only_in_Aquatics_and_Seagrasses.txt')
writeLines(genes_only_in_aquatics_and_seagrasses, fileConn)
close(fileConn)

@@

fileConn<-file('Genes_only_in_Aquatics_and_Seagrasses_and_Terrestrials.txt')
writeLines(genes_in_all, fileConn)
close(fileConn)
```

>>>>

fileConn<-file('data/Lost_present_gene_lists/Genes_only_in_Aquatics_and_Seagrasses.txt')
writeLines(genes_only_in_aquatics_and_seagrasses, fileConn)
close(fileConn)

@@

fileConn<-file('data/Lost_present_gene_lists/Genes_only_in_Aquatics_and_Seagrasses_and_Terrestrials.txt')
writeLines(genes_in_all, fileConn)
close(fileConn)
```
